Score-based tests of measurement invariance: Use in practice

### 2014-07-10 frontiers/IMPSpres-knitr.Rnw
update presentation according to Ed's comment.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@354 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}
  \frametitle{Visual Explanation of the Score-based Test}
  \begin{columns}
    \begin{column}{0.48\textwidth}     
      \begin{block}{Score}
        \resizebox{5.0cm}{!}{ 
          $
            \begin{blockarray}{cccccc}
              \text{}& \theta_{1} & \theta_{2} & \ldots 
                     &\textcolor{red}{\theta_{k}} & \text{age} \\
               \begin{block}{l(cccc)c}
                 x_{1} &  1.32  & -4.32 & \ldots & -2.34 & 10.5\\
                 x_{2} &  3.37 & 8.32 & \ldots & 63.45 & 11.0\\ 
                 x_{3} &  4.12 & 3.48 & \ldots & -3.11 & 11.3\\
                 x_{..} & \vdots & \vdots & \vdots & \vdots & 17.1\\ 
                 x_{n-1} &  12.34 & 13.32 & \ldots & 6.89 & 18.6\\
                 x_{n} & -5.78 & 3.50 & \ldots & 7.67 & 18.9\\
               \end{block}
            \end{blockarray} 
           $
          }
        \end{block}   
     \end{column}

     \begin{column}{0.48\textwidth}
          \begin{block}{Empirical Cumulative Score}
          \resizebox{5.0cm}{!}{
           $
            \begin{blockarray}{cccccc}
              \text{}& \theta_{1} & \theta_{2} & \ldots 
                     &\textcolor{red}{\theta_{k}} & \text{age} \\
               \begin{block}{l(cccc)c}
                 x_{1} &  1.32  & -4.32 & \ldots & -2.34 & 10.5 \\
                 x_{2} &  4.69 & 4.00 & \ldots & 61.11 & 11.0 \\
                 x_{3} &  8.81 & 7.48 & \ldots & 58.00 & 11.3 \\
                 x_{..} & \vdots & \vdots & \vdots & \vdots & 17.1 \\
                 x_{n-1} &  7.89 & 3.32 & \ldots & 4.91 & 18.6 \\
                 x_{n}& 0     &   0     & \ldots & 0 & 18.9 \\
               \end{block}
            \end{blockarray} 
           $
         }  
        \end{block}
      \end{column}
   \end{columns}
\end{frame}

@@

\begin{frame}
\begin{figure}
\tiny{\caption{Fluctuation processes for $\max\mathit{LM}_o$ statistic}}
\label{fig:ordres}
<<sctest-ord-graphics, fig.height=3.3, fig.width=5, echo=FALSE, results='hide'>>=
par(cex = 0.8)
sctest(restr, order.by = yg$agegroup, parm = 1:4, vcov = "info",
  functional = maxLMo, plot = TRUE,  
               ylim = c(0, 14), xlab = "Age group", 
               ylab = "LM statistics", main = expression(maxLM[o]))
@
\end{figure}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Visual Explanation of the Score-based Test}
  \begin{columns}
    \begin{column}{0.33\textwidth}     
      \begin{block}{Unordered Score}
        \resizebox{3.3cm}{!}{ 
          $
            \begin{blockarray}{lccccc}
              \text{obs} &\theta_{1} & \theta_{2} & \ldots 
                     &\textcolor{red}{\theta_{k}} & \text{age} \\
               \begin{block}{l(cccc)c}
                 &4.12 & 3.48 & \ldots & -3.11 & 11.3\\
                 &1.32  & -4.32 & \ldots & -2.34 & 10.5\\
                 &3.37 & 8.32 & \ldots & 63.45 & 11.0\\ 
                 &-5.78 & 3.50 & \ldots & 7.67 & 18.9\\
                 &\vdots & \vdots & \vdots & \vdots & 17.1\\ 
                 &12.34 & 13.32 & \ldots & 6.89 & 18.6\\              
               \end{block}
            \end{blockarray} 
           $
          }
        \end{block}   
     \end{column}

    \begin{column}{0.33\textwidth}     
      \begin{block}{Ordered Score}
        \resizebox{3.3cm}{!}{ 
          $
            \begin{blockarray}{lccccc}
              \text{obs}& \theta_{1} & \theta_{2} & \ldots 
                     &\textcolor{red}{\theta_{k}} & \text{age} \\
               \begin{block}{l(cccc)c}
                 x_{1} &  1.32  & -4.32 & \ldots & -2.34 & 10.5\\
                 x_{2} &  3.37 & 8.32 & \ldots & 63.45 & 11.0\\ 
                 x_{3} &  4.12 & 3.48 & \ldots & -3.11 & 11.3\\
                 x_{..} & \vdots & \vdots & \vdots & \vdots & 17.1\\ 
                 x_{n-1} &  12.34 & 13.32 & \ldots & 6.89 & 18.6\\
                 x_{n} & -5.78 & 3.50 & \ldots & 7.67 & 18.9\\
               \end{block}
            \end{blockarray} 
           $
          }
        \end{block}   
     \end{column}

     \begin{column}{0.33\textwidth}
          \begin{block}{\scriptsize{Empirical Cumulative Score}}
          \resizebox{3.3cm}{!}{
           $
            \begin{blockarray}{lccccc}
              \text{obs}& \theta_{1} & \theta_{2} & \ldots 
                     &\textcolor{red}{\theta_{k}} & \text{age} \\
               \begin{block}{l(cccc)c}
                 x_{1} &  1.32  & -4.32 & \ldots & -2.34 & 10.5 \\
                 x_{2} &  4.69 & 4.00 & \ldots & 61.11 & 11.0 \\
                 x_{3} &  8.81 & 7.48 & \ldots & 58.00 & 11.3 \\
                 x_{..} & \vdots & \vdots & \vdots & \vdots & 17.1 \\
                 x_{n-1} &  7.89 & 3.32 & \ldots & 4.91 & 18.6 \\
                 x_{n}& 0     &   0     & \ldots & 0 & 18.9 \\
               \end{block}
            \end{blockarray} 
           $
         }  
        \end{block}
      \end{column}
   \end{columns}
\end{frame}

@@

\begin{frame}
\begin{figure}
\tiny{\caption{Fluctuation processes for $\max\mathit{LM}_o$ statistic}}
\label{fig:ordres}
<<sctest-ord-graphics,  out.width="250px", out.height ="180px", echo=FALSE, results='hide'>>=
sctest(restr, order.by = yg$agegroup, parm = 1:4, vcov = "info",
  functional = maxLMo, plot = TRUE,  
               ylim = c(0, 14), xlab = "Age group", 
               ylab = "LM statistics", main = expression(maxLM[o]))
@
\end{figure}
\end{frame}
